This is an example of an EDA carried out using R using an isolated environment created using `renv`

```{r}
library(ggplot2)
library(dplyr)
library(palmerpenguins)
library(ggthemes)
```

```{r}
df <- penguins[complete.cases(penguins),]
head(df)
```

```{r}
ggplot(df, aes(x = bill_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm", se = F, color = "red") +
  theme_clean() +
  theme(legend.position = "top")
```

This shows a direct positive correlation between the two variables and some differences across species. In the modeling two methods are proposed. The first one is based off of a simple regression and shows an approximate fit to the data that is not very good (explains less than 40% of total variation in body mass). The second model employs a multiple linear regression with the categorical variable `species` to take into account the differences that might occur among the three different species in the sample. A graphical representation of this second model is given below.

```{r}
ggplot(df, aes(x = bill_length_mm, y = body_mass_g, color = species)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) +
  theme_clean() +
  theme(legend.position = "top")
```
